Project 1 for Complex Adaptive Systems

### 2018-02-18 paper.tex
Beginning of paper - not ready to be edited.  Also the pretty picture.

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

>>>>

\documentclass[conference]{IEEEtran}

\usepackage{graphicx}	
\usepackage{epstopdf}
\usepackage{color}
\usepackage{subcaption}
 \usepackage{float}
 \usepackage{wrapfig}

% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

For this project, we used the  model of growth define in INSERT REFERENCE that uses an logicistic growth model on a lattice of organisms coupled with influence from the entire population of organisms.  For each time step $n$, the size of population $i$ at time step $n$ is defined to be
\begin{eqnarray}
x_{i, n+1} = (1 - \epsilon) f_i(x_{i,n}) + \epsilon m_n, \ \ \ (i=1, 2, \ldots N)
\end{eqnarray}
Here $N$ is the number of time steps, $n$ is the current time step (or generation), and $\epsilon$ is the coupling strength of the model to the entire lattice of organisms.   Here the the local growth dynamics of each population $i$ is defined by 
\begin{eqnarray}
f_i(x_{i,n}) = r_i x_{i,n} (1 - {x_{i,n} \over K})
\end{eqnarray}
Here $r_i$ is the reproductive fitness of population $i$ and $K$ is the carrying capacity.

We model the state of the entire lattice at time $n$ is an average of the states of all the populations.  This is called the instantaneous mean field and defined to be
\begin{eqnarray}
M_n = { 1 \over N} \sum _{j=1}^N x_{j,n}
\end{eqnarray}

 The mean-field $m_n$ is a measure of how the individual populations are growing at any time-step $j$.  It is defined to be 
 \begin{eqnarray}
 m_n = {1 \over N} \sum_j^N f_j(x_{j,n})
\end{eqnarray}

The influence of $m_i$ on the entire system is quantified by the parameter $\epsilon$, the coupling strength.

To do our simulation,  we set the carrying capacity $K$ to be 100 for all populations $i$, the number of populations $N = 1000$ and use $10000$ time steps.   We set the initial population size $x_i, 0$ to be $1$.   We also select a random fitness $r_i$ for each population $i$.

% Figure for part 2
 \begin{figure}[H]
 \centering
    \includegraphics[width=90mm]{prettypicture}

    \caption{ Return map for selected values of  the global coupling strength $\epsilon$:  $\epsilon =0$ (red), $\epsilon = 0.1$ (blue), $\epsilon = 0.25$ (orange), $\epsilon = 0.225$ (aqua), $\epsilon = 0.25$ (dark green), $\epsilon = 3 $ (stars) and $\epsilon = 4$ (black)}
\end{figure}
